---
title: "Walmart Taxonomy API Practice"
author: Scott Reeves
#theme: NULL
output: 
  html_document: 
    css: custom.css
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r knitr, include=FALSE}
knitr::opts_chunk$set(comment="#>")
```

# Setup

```{r}

library(jsonlite)
library(tidyverse) #for glimpse
#library(purrr)

```

# Get API key

```{r}
key = getOption("api_key")
```

# Setup URL to get data

```{r}

taxonomy_url <- paste("http://api.walmartlabs.com/v1/taxonomy?apiKey=", key, "&format=json", sep="")

```

# About Walmart's Taxonomy API

https://developer.walmartlabs.com/docs/read/Taxonomy_API

Taxonomy API exposes the category taxonomy used by walmart.com to categorize items. It describes three levels as available on Walmart.com.
*Departments
*Categories
*Sub-categories

It is possible to specify the exact category as a parameter when using any of the API's below:

* Search
* Data feeds 
* Special feeds - [Pre-order, Best sellers, Rollbacks, Clearance and Special buys]

For example, Search API can be restricted to search within a category by supplying id as per the taxonomy. Similarly, Feed API can be used to download category specific feeds by specifying a category id.

For the Taxonomy API, the only parameter you need to specify is "format" (either json or xml)
taxonomy_url <- "http://api.walmartlabs.com/v1/taxonomy?apiKey=[Your API Key Here]&format=json".

# Helpful references:

http://r4ds.had.co.nz/hierarchy.html 

https://blog.exploratory.io/working-with-json-data-in-very-simple-way-ad7ebcc0bb89

# Read in the taxonomy data (JSON format)

```{r}
# taxonomy_data <- jsonlite::fromJSON(taxonomy_url, flatten = TRUE)

data <- as.data.frame(jsonlite::fromJSON("taxonomy.json", flatten = TRUE))

```

#Start testing and exploring

```{r}
head(data)
```


```{r}
dept_names    <- data$categories.name
dept_ids      <- data$categories.id
dept_paths    <- data$categories.path
dept_children <- data$categories.children


typeof(dept_names)
class(dept_names)
str(dept_names)

```

```{r}
data$categories.children[[1]]$name
```

```{r}
as.data.frame(data$categories.children[[1]]$children[[1]])
```

```{r}
arts <- dept_names[[1]]
arts
```

```{r}
arts_children <- data$categories.children[[1]]$children[[1]][[2]]

arts_children

```

```{r}
tmp.df <- as.data.frame(cbind(arts, arts_children))

tmp.df
```


Articulate the nested lists

```{r}

#outer list 0

glimpse(data)


```

Start setting up a vector of the column names, then append it for each list layer

```{r}
columns <- c("dept.id", "dept.name", "dept.path")

```

```{r}

#inner list 1

glimpse(data$categories.children[[4]])

```

```{r}
columns <- c(columns, "cat.id", "cat.name", "cat.path")

```


```{r}

#inner list 2

glimpse(data$categories.children[[2]]$children[[3]])

```

```{r}
columns <- c(columns, "subcat.id", "subcat.name", "subcat.path")
```

Start to identify the pattern to later use in a loop

```{r}
dep_id.1         <- data$categories.id[[1]]
dep_name.1       <- data$categories.name[[1]]
dep_path.1       <- data$categories.path[[1]]


cat_id.1         <- data$categories.children[[1]]$id[[1]]
cat_name.1       <- data$categories.children[[1]]$name[[1]]
cat_path.1       <- data$categories.children[[1]]$path[[1]]
subcat_id.1      <- data$categories.children[[1]]$children[[1]]$id
subcat_name.1    <- data$categories.children[[1]]$children[[1]]$name
subcat_path.1    <- data$categories.children[[1]]$children[[1]]$path

```

```{r}
categories.df <- as.data.frame(cbind(dep_id.1, dep_name.1, dep_path.1, cat_id.1, cat_name.1, cat_path.1, subcat_id.1, subcat_name.1, subcat_path.1))
names(categories.df) <- columns

```

```{r}
cat_id.2         <- data$categories.children[[1]]$id[[2]]
cat_name.2       <- data$categories.children[[1]]$name[[2]]
cat_path.2       <- data$categories.children[[1]]$path[[2]]
subcat_id.2      <- data$categories.children[[1]]$children[[2]][[1]]
subcat_name.2    <- data$categories.children[[1]]$children[[2]][[2]]
subcat_path.2    <- data$categories.children[[1]]$children[[2]][[3]]

#same as

cat_id.2         <- data$categories.children[[1]]$id[[2]]
cat_name.2       <- data$categories.children[[1]]$name[[2]]
cat_path.2       <- data$categories.children[[1]]$path[[2]]
subcat_id.2      <- data$categories.children[[1]]$children[[2]]$id
subcat_name.2    <- data$categories.children[[1]]$children[[2]]$name
subcat_path.2    <- data$categories.children[[1]]$children[[2]]$path

```

```{r}
data$categories.children[[1]]$children[[2]][[1]]
```


```{r}
data$categories.children[[1]]$children[[5]][[2]]
```

```{r}
data$categories.children[[1]]$children[[2]][[1]] == data$categories.children[[1]]$children[[2]]$id
```


```{r}
categories.tmp.df <- as.data.frame(cbind(dep_id.1, dep_name.1, dep_path.1, cat_id.2, cat_name.2, cat_path.2, subcat_id.2, subcat_name.2, subcat_path.2))
names(categories.tmp.df) <- columns

```

```{r}
categories.df <- rbind(categories.df, categories.tmp.df)
```


Start setting up a loop, starting with an inner list level 2 (the most inner level)

For the length of the list of children in each category (there are 22 children (22 categories, each containing a number of subcategories) of the first of 31 departments)

```{r}
length(data$categories.children[[1]]$children)
```

```{r}
checkfornull <- function(val){
  
  if(!is.null(val)){
    return(val)
  }else{
    return(NA)
  }
}
```

THIS WORKS. NEED TO ADD OUTER FOR LOOP FOR DEPARTMENTS.

```{r}


#assign the department values to its variables and hold them until all the department's children are processed

dep_id.1         <- data$categories.id[[1]]
dep_name.1       <- data$categories.name[[1]]
dep_path.1       <- data$categories.path[[1]]

#assign the first set of category and subcategory values

cat_id.1         <- data$categories.children[[1]]$id[[1]]
cat_name.1       <- data$categories.children[[1]]$name[[1]]
cat_path.1       <- data$categories.children[[1]]$path[[1]]
subcat_id.1      <- data$categories.children[[1]]$children[[1]]$id
subcat_name.1    <- data$categories.children[[1]]$children[[1]]$name
subcat_path.1    <- data$categories.children[[1]]$children[[1]]$path

#initialize the data frame

categories.df.2 <- as.data.frame(cbind(dep_id.1, dep_name.1, dep_path.1, cat_id.1, cat_name.1, cat_path.1, subcat_id.1, subcat_name.1, subcat_path.1))
names(categories.df.2) <- columns

#loop through each of the department's children and append the rows to the cumulative dataframe

for (j in 2:length(data$categories.children[[1]]$children)) {
  
  cat_id         <- data$categories.children[[1]]$id[[j]]
  cat_name       <- data$categories.children[[1]]$name[[j]]
  cat_path       <- data$categories.children[[1]]$path[[j]]
  subcat_id      <- checkfornull(data$categories.children[[1]]$children[[j]][[1]])
  subcat_name    <- checkfornull(data$categories.children[[1]]$children[[j]][[2]])
  subcat_path    <- checkfornull(data$categories.children[[1]]$children[[j]][[3]])
  
  #temp df
  
  categories.tmp.df.2 <- as.data.frame(cbind(dep_id.1, dep_name.1, dep_path.1, cat_id, cat_name, cat_path, subcat_id, subcat_name, subcat_path))
names(categories.tmp.df.2) <- columns

  #row bind
  
  categories.df.2 <- rbind(categories.df.2, categories.tmp.df.2)
}

```


```{r}
data$categories.children[[8]]$children[[14]]
data$categories.children[[8]]$children[[14]][[2]][[1]]
data$categories.children[[8]]$children[[14]][[2]][[2]]

```

```{r}
# i
length(data$categories.children)
```

```{r}
data$categories.children[10]
```


```{r}
# j
length(data$categories.children[[1]]$children)
```

```{r}
data$categories.children

```


```{r}
# k
length(data$categories.children[[10]]$children[[1]][[1]])
```

```{r}
length(data$categories.children[[1]]$children[[3]])

```

```{r}

data$categories.children[[10]]

```

```{r}
length(data$categories.children[[10]]$id)
```

```{r}
data$categories.children[[10]]$name[[1]]
```

```{r}
data$categories.children[[1]]$children[[1]]$name[[1]]

```

```{r}

columns.4 <- c("dept.id", "dept.name", "dept.path", "cat.id", "cat.name", "cat.path", "subcat.id", "subcat.name", "subcat.path")

#loop through each department

for (i in 1:length(data$categories.children)) {
  
  dep_id             <- checkfornull(data$categories.id[[i]])
  dep_name           <- checkfornull(data$categories.name[[i]])
  dep_path           <- checkfornull(data$categories.path[[i]])
  
  for (j in 1:length(data$categories.children[[i]]$id)) {
    cat_id           <- checkfornull(data$categories.children[[i]]$id[[j]])
    cat_name         <- checkfornull(data$categories.children[[i]]$name[[j]])
    cat_path         <- checkfornull(data$categories.children[[i]]$path[[j]])
    
    #----
    
    if (length(data$categories.children[[i]]$children[[j]][[1]]) > 0 ){
      
      for (k in 1:length(data$categories.children[[i]]$children[[j]][[1]])) {
        subcat_id      <- checkfornull(data$categories.children[[i]]$children[[j]]$id[[k]])
        subcat_name    <- checkfornull(data$categories.children[[i]]$children[[j]]$name[[k]])
        subcat_path    <- checkfornull(data$categories.children[[i]]$children[[j]]$path[[k]])
      
        } #close k
      
      } #close if
      
      else{
            
      subcat_id      <- NA
      subcat_name    <- NA
      subcat_path    <- NA
      
      } #close else
    
    #----
    
    # print(i)
    # print(j)
    # print(k)
    
    if(i == 1 & j == 1){
      categories.df.4           <- as.data.frame(cbind(dep_id, dep_name, dep_path, cat_id, cat_name, cat_path, subcat_id, subcat_name, subcat_path))
      names(categories.df.4)    <- columns.4
    } #close if
    else{
      #temp df
      categories.tmp.df.4        <- as.data.frame(cbind(dep_id, dep_name, dep_path, cat_id, cat_name, cat_path, subcat_id, subcat_name, subcat_path))
      names(categories.tmp.df.4) <- columns.4
      #row bind
      categories.df.4 <- rbind(categories.df.4, categories.tmp.df.4)
    } #close else 
  } #close j
} #close i


```

```{r}

#loop through each department

for (i in 1:length(data$categories.children)) {
  
  dep_id             <- checkfornull(data$categories.id[[i]])
  dep_name           <- checkfornull(data$categories.name[[i]])
  dep_path           <- checkfornull(data$categories.path[[i]])
  
  #loop through each of the department's children (categories) 
  
  for (j in 1:length(data$categories.children[[i]]$children)) {
  
    cat_id           <- checkfornull(data$categories.children[[i]]$id[[j]])
    cat_name         <- checkfornull(data$categories.children[[i]]$name[[j]])
    cat_path         <- checkfornull(data$categories.children[[i]]$path[[j]])
    
    #loop through each of the categories' children (subcategories) and initialize or append the dataframe
    
    # accomodate categories which have no subcategories
    
    if (length(data$categories.children[[i]]$children[[j]][[1]]) > 0 ){
      
      for (k in 1:length(data$categories.children[[i]]$children[[j]][[1]])) {
        subcat_id      <- checkfornull(data$categories.children[[i]]$children[[j]]$id[[k]])
        subcat_name    <- checkfornull(data$categories.children[[i]]$children[[j]]$name[[k]])
        subcat_path    <- checkfornull(data$categories.children[[i]]$children[[j]]$path[[k]])
      
        } #close k
      
      } #close if
      
      else{
            
      subcat_id      <- NA
      subcat_name    <- NA
      subcat_path    <- NA
      
      } #close else
     
    #if it is the first department and the first category, then initialize the data frame
      
    if(i == 1 & j == 1 & k == 1){
      
      categories.df.3 <- as.data.frame(cbind(dep_id, dep_name, dep_path, cat_id, cat_name, cat_path, subcat_id, subcat_name, subcat_path))
      names(categories.df.3) <- columns
      
      } #close if
      
      else{
        
        #temp df
        
        categories.tmp.df.3 <- as.data.frame(cbind(dep_id, dep_name, dep_path, cat_id, cat_name, cat_path, subcat_id, subcat_name, subcat_path))
        names(categories.tmp.df.3) <- columns
  
        #row bind
    
        categories.df.3 <- rbind(categories.df.3, categories.tmp.df.3) 
        
        } #close else
  } #close j
} #close i

```

```{r}
data$categories.children[[31]]$children[[10]][[1]][[2]]
```


```{r}
tmp.df.1 <- as.data.frame(cbind(data$categories.name[[1]],data$categories.children[[1]]$name[[1]],data$categories.children[[1]]$children[[1]][[2]]))

names(tmp.df.1) <- c("dept.name", "category.name", "subcat.name")

tmp.df.1
```

```{r}
tmp.df.2 <- as.data.frame(cbind(data$categories.name[[1]],data$categories.children[[1]]$name[[1]],data$categories.children[[1]]$children[[2]][[2]]))

names(tmp.df.2) <- c("dept.name", "category.name", "subcat.name")

tmp.df.2

```

```{r}
collector.df <- rbind(tmp.df.1, tmp.df.2)

collector.df

```











```{r}
# Access (get) the top level object name
level_1_names <- as.vector(names(taxonomy_data))
level_2_names <- as.vector(names(taxonomy_data$categories))

names(df) <- level_2_names

for (name in level_2_names) {
  
  print(name)
  
}

df
```

```{r}
# Access (get) the attribute(column) names of the "categories"-level object

dept.names <- names(taxonomy_data$categories)
```




```{r}
# Show the class of the categories-children object

class(taxonomy_data$categories$children)
```

```{r}
# Get the number [length of the vector(list)] of the second level "children"

length(taxonomy_data$categories$children)
```

```{r}
# Access (get) the attribute(column) names of the "categories"-"name"-level object

taxonomy_data$categories$name
```


```{r}
taxonomy_data$categories$path
```

```{r}
taxonomy_data$categories$children[[7]]$path
```

```{r}
taxonomy_data$categories$children[[7]]$name
```


```{r}
taxonomy_data[[1]]
```


```{r}
taxonomy_data[["categories"]]
```


```{r}
dept_names <- sapply(taxonomy_data, function(x) x[[2]])
head(dept_names)
```

```{r}
dept_names <- sapply(taxonomy_data, function(x) x[2])

```

```{r}
dept_names <- sapply(taxonomy_data, function(x) x[[2]])
dept_names
```

```{r}

```


```{r}
taxonomy_data[[1]][[4]][[1]][[4]][[1]][[2]]
```

```{r}
taxonomy_data$categories$children[[1]]["name"]
```

```{r}
category_names <- sapply(taxonomy_data$categories$children, function(x) x[2])
category_names
```

```{r}
subcategory_names_test1 <- sapply(taxonomy_data$categories$children[[1]], function(x) x[2])
subcategory_names_test1
```

```{r}
subcategory_names_test2 <- sapply(taxonomy_data$categories$children[1], function(x) x[2])
subcategory_names_test2
```


```{r}
taxonomy_data$categories$children[[2]][[3]]

```

```{r}

output1 <- taxonomy_data$categories$children[[1]]["name"]

for (i in 1:length(taxonomy_data$categories$children)) {
  
  tmp <- sapply(taxonomy_data$categories$children[i], function(x) x[2])
  
  output1 <- rbind(output1, tmp)
  
}

output1

```

```{r}
View(output1)
```

```{r}

subcatname <- taxonomy_data$categories$children[[1]]["name"]
subcatpath <- taxonomy_data$categories$children[[1]]["path"]


for (i in 1:length(taxonomy_data$categories$children)) {
  
  tmp <- sapply(taxonomy_data$categories$children[i], function(x) x[2])
  
  subcatname <- rbind(subcatname, tmp)
  
}

for (i in 1:length(taxonomy_data$categories$children)) {
  
  tmp <- sapply(taxonomy_data$categories$children[i], function(x) x[3])
  
  subcatpath <- rbind(subcatpath, tmp)
  
}

output2 <- cbind(subcatpath, subcatname)

output2

```

```{r}
names(taxonomy_data$categories)[2]


```


```{r}

df <- data.frame()


for (name in names(taxonomy_data$categories)) {
  
  dept = names(taxonomy_data$categories[name])
  
  #print (dept)
  
  #cbind(df, dept)
  cbind(df, dept_name = dept)
  
}

df

```







```{r}
testdf <- data.frame(
  name = taxonomy_data$categories$children[[2]][[2]],
  path = taxonomy_data$categories$children[[2]][[3]])

testdf
```

```{r}
View(testdf)
```


```{r}
df <- data.frame(
  "dept_id"   = taxonomy_data$categories$id,
  "dept_name" = taxonomy_data$categories$name,
  "dept_path" = taxonomy_data$categories$path,
  "subcat_name"  = output2$name
  
)

df
```



Keep working on this, using apply. 
Try https://stackoverflow.com/questions/15059076/call-apply-like-function-on-each-row-of-dataframe-with-multiple-arguments-from-e?utm_medium=organic&utm_source=google_rich_qa&utm_campaign=google_rich_qa

```{r}

testdf2 <- testdf <- data.frame(
  name = taxonomy_data$categories$children[[1]][[3]],
  path = taxonomy_data$categories$children[[1]][[2]])

for (i in 2:length(taxonomy_data$categories$children)) {
  
  tmp <- apply(taxonomy_data$categories$children[i], 2, function(x) x[2])
  
  testdf2 <- rbind(testdf2, tmp)
  
}

testdf2

```


























