---
title: "Walmart Taxonomy API Practice"
author: Scott Reeves
#theme: NULL
output: 
  html_document: 
    css: custom.css
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r knitr, include=FALSE}
knitr::opts_chunk$set(comment="#>")
```

# Setup

```{r}

library(jsonlite)
library(tidyverse)
library(purrr)

```

# Get API key

```{r}
key = getOption("api_key")
```

# Setup URL to get data

```{r}

taxonomy_url <- paste("http://api.walmartlabs.com/v1/taxonomy?apiKey=", key, "&format=json", sep="")

```

# About Walmart's Taxonomy API

https://developer.walmartlabs.com/docs/read/Taxonomy_API

Taxonomy API exposes the category taxonomy used by walmart.com to categorize items. It describes three levels as available on Walmart.com.
*Departments
*Categories
*Sub-categories

It is possible to specify the exact category as a parameter when using any of the API's below:

* Search
* Data feeds 
* Special feeds - [Pre-order, Best sellers, Rollbacks, Clearance and Special buys]

For example, Search API can be restricted to search within a category by supplying id as per the taxonomy. Similarly, Feed API can be used to download category specific feeds by specifying a category id.

For the Taxonomy API, the only parameter you need to specify is "format" (either json or xml)
taxonomy_url <- "http://api.walmartlabs.com/v1/taxonomy?apiKey=[Your API Key Here]&format=json".

# Helpful references:

http://r4ds.had.co.nz/hierarchy.html 

https://blog.exploratory.io/working-with-json-data-in-very-simple-way-ad7ebcc0bb89

# Read in the taxonomy data (JSON format)

```{r}
# taxonomy_data <- jsonlite::fromJSON(taxonomy_url, flatten = TRUE)

taxonomy_data <- jsonlite::fromJSON("taxonomy.json", flatten = TRUE)

```

## Explore the taxonomy data

https://cran.r-project.org/doc/manuals/r-release/R-intro.html#Function-and-variable-index

```{r}

explore_object <- function(object) {
  
  obj_type    = typeof(object)
 #obj_class   = class(object)
  obj_length  = length(object)
  obj_names   = names(object)
 #obj_str     = str(object)
  obj_dim     = dim(object)
  obj_summary = summary(object)
  #length
  
  print (paste("object type:",       (obj_type),    sep = " "))
 #print (paste("object class:",      (obj_class),   sep = " "))
  print (paste("object length:",     (obj_length),  sep = " "))
  print (paste("object names:",      (obj_names),   sep = " "))
 #print (paste("object structure:",  (obj_str),     sep = " "))
  print (paste("object dimensions:", (obj_dim),     sep = " "))
  print ("object summary:")
  summary(object)

  

}

```


```{r}

explore_object(taxonomy_data$categories)
```

```{r}
explore_object(taxonomy_data$categories$name)
```

```{r}
View(taxonomy_data)
```

```{r}
# Access (get) the top level object name
names(taxonomy_data)
```

```{r}
# Access (get) the attribute(column) names of the "categories"-level object

dept.names <- names(taxonomy_data$categories)
```

```{r}
df <- data.frame(dept.names[1],
                 dept.names[2])
df
```


```{r}
# Show the class of the categories-children object

class(taxonomy_data$categories$children)
```

```{r}
# Get the number [length of the vector(list)] of the second level "children"

length(taxonomy_data$categories$children)
```

```{r}
# Access (get) the attribute(column) names of the "categories"-"name"-level object

taxonomy_data$categories$name
```


```{r}
taxonomy_data$categories$path
```

```{r}
taxonomy_data$categories$children[[7]]$path
```

```{r}
taxonomy_data$categories$children[[7]]$name
```


```{r}
taxonomy_data[[1]]
```


```{r}
taxonomy_data[["categories"]]
```


```{r}
dept_names <- sapply(taxonomy_data, function(x) x[[2]])
head(dept_names)
```

```{r}
dept_names <- sapply(taxonomy_data, function(x) x[2])

```

```{r}
dept_names <- sapply(taxonomy_data, function(x) x[[2]])
dept_names
```

```{r}

```


```{r}
taxonomy_data[[1]][[4]][[1]][[4]][[1]][[2]]
```

```{r}
taxonomy_data$categories$children[[1]]["name"]
```

```{r}
category_names <- sapply(taxonomy_data$categories$children, function(x) x[2])
category_names
```

```{r}
subcategory_names_test1 <- sapply(taxonomy_data$categories$children[[1]], function(x) x[2])
subcategory_names_test1
```

```{r}
subcategory_names_test2 <- sapply(taxonomy_data$categories$children[1], function(x) x[2])
subcategory_names_test2
```


```{r}
taxonomy_data$categories$children[[2]][[3]]

```

```{r}

output1 <- taxonomy_data$categories$children[[1]]["name"]

for (i in 1:length(taxonomy_data$categories$children)) {
  
  tmp <- sapply(taxonomy_data$categories$children[i], function(x) x[2])
  
  output1 <- rbind(output1, tmp)
  
}

output1

```

```{r}
View(output1)
```

```{r}

subcatname <- taxonomy_data$categories$children[[1]]["name"]
subcatpath <- taxonomy_data$categories$children[[1]]["path"]


for (i in 1:length(taxonomy_data$categories$children)) {
  
  tmp <- sapply(taxonomy_data$categories$children[i], function(x) x[2])
  
  subcatname <- rbind(subcatname, tmp)
  
}

for (i in 1:length(taxonomy_data$categories$children)) {
  
  tmp <- sapply(taxonomy_data$categories$children[i], function(x) x[3])
  
  subcatpath <- rbind(subcatpath, tmp)
  
}

output2 <- cbind(subcatpath, subcatname)

output2

```

```{r}
names(taxonomy_data$categories)[2]


```


```{r}

df <- data.frame()


for (name in names(taxonomy_data$categories)) {
  
  dept = names(taxonomy_data$categories[name])
  
  #print (dept)
  
  #cbind(df, dept)
  cbind(df, dept_name = dept)
  
}

df

```







```{r}
testdf <- data.frame(
  name = taxonomy_data$categories$children[[2]][[2]],
  path = taxonomy_data$categories$children[[2]][[3]])

testdf
```

```{r}
View(testdf)
```


```{r}
df <- data.frame(
  "dept_id"   = taxonomy_data$categories$id,
  "dept_name" = taxonomy_data$categories$name,
  "dept_path" = taxonomy_data$categories$path,
  "subcat_name"  = output2$name
  
)

df
```



Keep working on this, using apply. 
Try https://stackoverflow.com/questions/15059076/call-apply-like-function-on-each-row-of-dataframe-with-multiple-arguments-from-e?utm_medium=organic&utm_source=google_rich_qa&utm_campaign=google_rich_qa

```{r}

testdf2 <- testdf <- data.frame(
  name = taxonomy_data$categories$children[[1]][[3]],
  path = taxonomy_data$categories$children[[1]][[2]])

for (i in 2:length(taxonomy_data$categories$children)) {
  
  tmp <- apply(taxonomy_data$categories$children[i], 2, function(x) x[2])
  
  testdf2 <- rbind(testdf2, tmp)
  
}

testdf2

```


























