---
title: "Walmart Taxonomy API Practice"
author: Scott Reeves
#theme: NULL
output: 
  html_document: 
    css: custom.css
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r knitr, include=FALSE}
knitr::opts_chunk$set(comment="#>")
```


```{r}
# Setup
library(jsonlite)
library(tidyverse)
#library(purrr)
```

```{r}
# ingest api key
key = getOption("api_key")
```


```{r}
# config taxonomy url

taxonomy_url <- paste("http://api.walmartlabs.com/v1/taxonomy?apiKey=", key, "&format=json", sep="")
```

## Taxonomy API

https://developer.walmartlabs.com/docs/read/Taxonomy_API

Taxonomy API exposes the category taxonomy used by walmart.com to categorize items. It describes three levels as available on Walmart.com.
*Departments
*Categories
*Sub-categories

It is possible to specify the exact category as a parameter when using any of the API's below:

* Search
* Data feeds 
* Special feeds - [Pre-order, Best sellers, Rollbacks, Clearance and Special buys]

For example, Search API can be restricted to search within a category by supplying id as per the taxonomy. Similarly, Feed API can be used to download category specific feeds by specifying a category id.

For the Taxonomy API, the only parameter you need to specify is "format" (either json or xml)
taxonomy_url <- "http://api.walmartlabs.com/v1/taxonomy?apiKey=[Your API Key Here]&format=json".

### Helpful references:

http://r4ds.had.co.nz/hierarchy.html 

https://blog.exploratory.io/working-with-json-data-in-very-simple-way-ad7ebcc0bb89

```{r}
txcats <- jsonlite::fromJSON(taxonomy_url)
```

```{r}
names(txcats)
```

```{r}
names(txcats$categories)
```

```{r}
length(txcats$categories$children)
```

```{r}
flat_data <- jsonlite::flatten(txcats$categories, recursive = TRUE)

flat_data

```

```{r}

```




